Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-26 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors \cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} 
and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} in healthy and impaired cardiomyocytes. After measuring the 
topography with SICM the nanopipette could be moved to

>>>>

SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors 
\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} 
in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. After measuring the 
topography with SICM the nanopipette could be moved to
